Automated Example Oriented REST API Documentation

### 2017-08-16 case_study/case_study.tex
all chapters added
more spell checks

\chapter{A Case Study of Web API Evolution}

%\author{\IEEEauthorblockN{S M Sohan, Craig Anslow, Frank Maurer
%\IEEEauthorblockA{Department of Computer Science\\
%University of Calgary,
%Calgary, Alberta T2N 1N4\\ Email: \{smsohan, craig.anslow, frank.maurer\}@ucalgary.ca }
%}}

%\maketitle

@@

%\begin{IEEEkeywords}
%Case Study; RESTful, SOAP, Web API Evolution; WSDL
%\end{IEEEkeywords}

%\IEEEpeerreviewmaketitle

@@

The first author of this paper read the the API homepages and followed relevant hyperlinks to find answers to RQ1. A summary of the strategies were presented to the co-authors, which was used to categorize Web API versioning strategies into groups. Web API homepages contain changelogs and links to API references which were used to find answers to RQ2.

@@

\textbf{Endpoint} - URLs to access the the API.
\textbf{Resource} - An input or output object. For example, comment, photo, etc.
\textbf{Method} - An API operation on a resource. e.g. post a comment.
\textbf{Field} - An attribute of the resource. e.g. timestamps of a comment.
\textbf{FieldValue} - Possible value for a field. For example: a timestamp value of January 1, 2015.
\textbf{Error} - Error cases. e.g. not found error.
\textbf{Authentication} - Authentication methods. e.g. HTTP Basic authentication.

@@

We analyzed the API user forums and newsboards to find answers to RQ3. Messages in these sources were filtered to focus on the evolution of Web APIs. These data sources provided the perspectives of both the developers and users of Web APIs. To find evolution related messages, based on trial search runs, full text search features on the forums were used to search for these keywords: version, release, migration, breaking, deprecate, change.

>>>>

\chapter{A Case Study of Web API Evolution}
\label{chapter:case_study}

@@

@@

The first author of this paper read the API homepages and followed relevant hyperlinks to find answers to RQ1. A summary of the strategies were presented to the co-authors, which was used to categorize Web API versioning strategies into groups. Web API homepages contain changelogs and links to API references which were used to find answers to RQ2.

@@

\textbf{Endpoint} - URLs to access the API.
\textbf{Resource} - An input or output object. For example, comment, photo, etc.
\textbf{Method} - An API operation on a resource. e.g. post a comment.
\textbf{Field} - An attribute of the resource. e.g. timestamps of a comment.
\textbf{FieldValue} - Possible value for a field. For example: a timestamp value of January 1, 2015.
\textbf{Error} - Error cases. e.g. not found error.
\textbf{Authentication} - Authentication methods. e.g. HTTP Basic authentication.

@@

We analyzed the API user forums and news boards to find answers to RQ3. Messages in these sources were filtered to focus on the evolution of Web APIs. These data sources provided the perspectives of both the developers and users of Web APIs. To find evolution related messages, based on trial search runs, full text search features on the forums were used to search for these keywords: version, release, migration, breaking, deprecate, change.

### 2017-08-16 cisco_study/cisco_study.tex
fix the label/caption order
adds all 5 papers, reasonable ok formatted
structurally complete, sans abstract / introduction / conclusion
all chapters added
more spell checks

\section{Automated Example Oriented REST API Documentation at Cisco}

%\author{\IEEEauthorblockN{S M Sohan}
%\IEEEauthorblockA{
%Security Group\\
%Cisco Systems Ltd.\\
%Calgary, Canada\\
%sosohan@cisco.com}
%\and
%\IEEEauthorblockN{Craig Anslow}
%\IEEEauthorblockA{
%Department of Computer Science\\
%Middlesex University\\
%London, United Kingdom\\
%c.anslow@mdx.ac.uk}
%\and
%\IEEEauthorblockN{Frank Maurer}
%\IEEEauthorblockA{
%Department of Computer Science\\
%University of Calgary\\
%Calgary, Canada\\
%frank.maurer@ucalgary.ca}
%}

@@

%\begin{IEEEkeywords}
%API; REST; Documentation; Tool; Case study; Test; Automation; HTTP; Web API;

%\end{IEEEkeywords}

@@

\begin{figure*}
  \begin{subfigure}[b]{\textwidth}
    \centering{
      \includegraphics[keepaspectratio, height=0.4\textheight]{overview.png}
    }
    \label{fig:screenshot_overview}
    \caption{API Overview in SpyREST}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \centering{
      \includegraphics[keepaspectratio, height=0.4\textheight]{fields.png}
    }
    \label{fig:screenshot_fields}
    \caption{SpyREST Analyzed API Structure}
  \end{subfigure}
\end{figure*}
\begin{figure*}\ContinuedFloat
  \begin{subfigure}[t]{0.5\textwidth}
    \centering{
      \includegraphics[keepaspectratio, width=\textwidth]{request.png}
    }
    \label{fig:screenshot_request}
    \caption{SpyREST Recorded API Request}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \centering{
      \includegraphics[keepaspectratio, width=\textwidth]{response.png}
    }
    \label{fig:screenshot_response}
    \caption{SpyREST Recorded API Response}
  \end{subfigure}

  \caption{Screenshots of the REST API documentation from Cisco using SpyREST}
  \label{fig:screenshot}
\end{figure*}

@@

The next step in the lifecycle of the API documentation is in the automated build server where the test suite is executed against a deployed API on a staging server through a SpyREST proxy. This promotes the REST API documentation from the developer workstation to a shared instance that is used by the quality assurance engineers, product management, and the peer developers to verify against the acceptance criteria. This often results in several loops between the developer workstations and the staging servers until the API and its documentation meets the acceptance criteria. During the team retrospective following the API production release, the following comment was captured in the meeting notes by one of the QA engineers (QA1):  \textbf{``Up-to-date documentation using SpyREST helped developing and collecting lots of input about the API in small pieces during the weekly meetings before production release''}. The API developers and quality assurance engineers add any custom content as needed to describe complex API concepts and prerequisites that aren't captured in the automated examples.

The next step in the lifecycle of the API is a release to one or more of the production environments that customers use. With the production release of an updated API, its documentation is automatically promoted from the staging environment to production. The promotion of the documentation is a three-step process. First, the data from the staging server is exported in a portable archive file. Then, a transformation is performed to update staging specific data such as URLs, email domains, and hostnames within the archive to match the desired production environment. Finally, the transformed archive is published to production as a read-only artifact.

@@

When API version v1 is launched, all the functional tests for v0 are run on a loop, once per version. This code reuse minimizes the effort required to document multiple versions of the same API action when the API versions are backward compatible. The rest of the lifecycle steps follow similar process as the documentation of a new API action.

>>>>

\chapter{Automated Example Oriented REST API Documentation at Cisco}
\label{chapter:cisco_study}

@@

@@

\begin{figure*}
  \begin{subfigure}[b]{\textwidth}
    \centering{
      \includegraphics[keepaspectratio, height=0.4\textheight]{overview.png}
    }
    \caption{API Overview in SpyREST}
    \label{fig:screenshot_overview}
  \end{subfigure}

  \begin{subfigure}[b]{\textwidth}
    \centering{
      \includegraphics[keepaspectratio, height=0.4\textheight]{fields.png}
    }
    \caption{SpyREST Analyzed API Structure}
    \label{fig:screenshot_fields}
  \end{subfigure}
\end{figure*}
\begin{figure*}\ContinuedFloat
  \begin{subfigure}[t]{0.5\textwidth}
    \centering{
      \includegraphics[keepaspectratio, width=\textwidth]{request.png}
    }
    \caption{SpyREST Recorded API Request}
    \label{fig:screenshot_request}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \centering{
      \includegraphics[keepaspectratio, width=\textwidth]{response.png}
    }
    \caption{SpyREST Recorded API Response}
    \label{fig:screenshot_response}
  \end{subfigure}

  \caption{Screenshots of the REST API Documentation from Cisco using SpyREST}
  \label{fig:screenshot}
\end{figure*}

@@

The next step in the life cycle of the API documentation is in the automated build server where the test suite is executed against a deployed API on a staging server through a SpyREST proxy. This promotes the REST API documentation from the developer workstation to a shared instance that is used by the quality assurance engineers, product management, and the peer developers to verify against the acceptance criteria. This often results in several loops between the developer workstations and the staging servers until the API and its documentation meets the acceptance criteria. During the team retrospective following the API production release, the following comment was captured in the meeting notes by one of the QA engineers (QA1):  \textbf{``Up-to-date documentation using SpyREST helped developing and collecting lots of input about the API in small pieces during the weekly meetings before production release''}. The API developers and quality assurance engineers add any custom content as needed to describe complex API concepts and prerequisites that aren't captured in the automated examples.

The next step in the life cycle of the API is a release to one or more of the production environments that customers use. With the production release of an updated API, its documentation is automatically promoted from the staging environment to production. The promotion of the documentation is a three-step process. First, the data from the staging server is exported in a portable archive file. Then, a transformation is performed to update staging specific data such as URLs, email domains, and host names within the archive to match the desired production environment. Finally, the transformed archive is published to production as a read-only artifact.

@@

When API version v1 is launched, all the functional tests for v0 are run on a loop, once per version. This code reuse minimizes the effort required to document multiple versions of the same API action when the API versions are backward compatible. The rest of the life cycle steps follow similar process as the documentation of a new API action.
